---
title: "Linking survey to JHS database"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tmap)
library(spData)
library(tidyverse)
library(haven)
library(lubridate)
library(fastDummies)
library(reldist)
library(patchwork)
library(sjlabelled)
source("functions.R")
data(us_states)
data(us_states_df)
Sys.setlocale("LC_TIME", "en_US.UTF-8")
```

This file generates the Figure about the COVID-19 reminder and 
outputs a dataset with state-level numbers of confirmed cases 
in `data/corona_status_March-28.csv`.

# Reading data 

Reading data from Ipsos:
```{r message=FALSE, warning=FALSE}
wavedate_df <- tribble(~Wavemarker, ~wavedt,
                       4, "2020-3-18",  # Not to be used - No COVID-19 reminder
                       5, "2020-3-24",
                       6, "2020-3-25", 
                       7, "2020-3-26",
                       8, "2020-3-27",
                       9, "2020-3-30",
                       10,"2020-3-31",
                       11,"2020-4-1", 
                       12,"2020-4-2") %>% 
  mutate(wavedt = as.Date(wavedt))

ipsos <- haven::read_dta(here::here("data","processed", "ipsos_mmnyt_processed_release.dta")) %>%
 mutate( state = as.character(haven::as_factor(State_Recoded)),
         solidarity = 10 - prior_self_over_soc,
         inequality_aversion = luck_unfair_agree,
         redistribution = gov_reduce_inequality_agree,
         female = as.numeric(resp_gender==2),
         ) %>% left_join(wavedate_df) %>%
  filter(!is.na(wavedt))
```

I have downloaded the JHS covid-19 database of confirmed cases
```{r}
confirmed_US <- read_csv(here::here("data", "raw", "time_series_covid19_confirmed_US.csv"))
```
Reshaping the JHS data to a longer format that is easier to work with:
```{r}
confirmed_long <- confirmed_US %>% 
  pivot_longer(`1/22/20`:`5/4/20`, names_to="covid_date", values_to="n_confirmed") %>%
  mutate(cdate = mdy(covid_date)) %>% 
  group_by(Province_State, cdate) %>%
  summarize(confirmed = sum(n_confirmed))
```

We want to join by population (state level)
```{r}
population <- read_csv(url("https://www2.census.gov/programs-surveys/popest/datasets/2010-2019/state/detail/SCPRC-EST2019-18+POP-RES.csv")) %>% 
  janitor::clean_names() %>%
  dplyr::select(c("name", "popestimate2019")) %>%
  rename(state = name, pop2019 = popestimate2019) %>%
  filter(state != "United States")
```


# Merging outcomes
Restricting the set of regions to the states and DC, not the other
territories as well
```{r}
US_covid_outcomes <- confirmed_long 
long_data <- US_covid_outcomes %>% rename(state = Province_State) %>%
    right_join(population, by=c("state")) %>%
  mutate( confirmed_by_100_000 = confirmed/pop2019 * 100000) %>%
  filter( state %in% ipsos$state )
```

# Confirmed cases and survey period

```{r}
survey_period <- long_data %>% ggplot(aes(x=cdate, y=confirmed_by_100_000, 
                                 group=state)) +
  geom_rect(aes(xmin=as.Date("2020-03-24"),
                xmax=as.Date("2020-04-02"), 
                ymin=0, 
                ymax=Inf
                ), fill="grey80") +
  geom_line(alpha=0.5) +
  scale_x_date(limits = as.Date(c("2020-03-01", "2020-05-05"))) +
  theme_minimal() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) + 
  labs(y="# Confirmed / 100,000", 
       x=element_blank())
survey_period       
```


# The data needed for the PAP
The PAP specified that we would use the status per March 26 as reference for how
hard each state was hit by the virus, this was based on the idea that the 26th would
be the mid point of the survey. Instead the survey was a couple of days delayed,
and not March 28 is closer to the mid of the survey.
```{r}
corona_PAP <- US_covid_outcomes %>% 
  filter(cdate == "2020-03-28") %>%
  rename(state = Province_State) %>%
  right_join(population, by="state") %>% filter(!is.na(cdate))
corona_PAP %>% write_csv(here::here("data","corona_status_March-28.csv"))
```


# Correlation between subjective report and confirmed cases

Calculating state averages of the priming question to correlate with level confirmed
```{r}
primes <- ipsos %>% group_by(state) %>%
  summarize(mean_affected = weighted.mean(prime_affected, Weightvar, na.rm=TRUE),
            mean_estlength = weighted.mean(prime_weeks, Weightvar, na.rm=TRUE)) %>%
  left_join(corona_PAP, by="state") %>%
  mutate(confirmed_by_100_000 = confirmed/pop2019 * 100000)
```

Plotting the self report of how much the local community is affected against 
actual confirmed rate per March 28.
```{r}
p1 <- primes %>% ggplot(aes(x=confirmed_by_100_000, y=mean_affected)) + 
  scale_x_log10() + 
  geom_smooth(method='lm', color='black') + 
  geom_point(aes(size=pop2019), alpha=0.4) +
  theme_minimal() +
  labs(x="# Confirmed / 100,000 (March 28)",
       y="Mean degree affected") + 
  theme(legend.position = "none")
p1
```

Now a version that combines the Covid-19 data with survey period and 
the extent to which they are affected.

```{r}
survey_period + p1 + plot_annotation(tag_levels = "a")
ggsave(here::here("graphs","survey_period.pdf"), width=16, height=10, units="cm")
```
