---
title: "Multiple hypothesis testing for interaction effects"
author: "Erik Ø. Sørensen"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sandwich)
library(haven)
library(reldist)
library(boot)

source("functions.R")
load("Adjust.RData")
```


The point of this file is to calculate Romano-Wolf corrected p-values for all
the interaction effects for each of the 6 outcomes of Figure 1 in the main paper
and for the two policy preferences (redistribution and health care). 

Here is a global variable set with the number of bootstrap replications:
```{r}
NBOOTSTRAPS <- 9999
```

The simulations are written to be calculated on a powerful linux computer (hence the
` parallel="multicore", ncpus=30` arguments given to `boot` in all the simulation functions. For running
on a windows computer (or one less powerful), this should be modified or deleted (but this
program will then run quite slowly). 

# Reading data
Reading data from Ipsos:
```{r message=FALSE, warning=FALSE}
wavedate_df <- tribble(~Wavemarker, ~wavedt,
                       4, "2020-3-18", # Not to be used - No COVID-19 reminder
                       5, "2020-3-24",
                       6, "2020-3-25", 
                       7, "2020-3-26",
                       8, "2020-3-27",
                       9, "2020-3-30",
                       10,"2020-3-31",
                       11,"2020-4-1", 
                       12,"2020-4-2") %>% 
  mutate(wavedt = as.Date(wavedt))

ipsos <- haven::read_dta(here::here("data","processed", "ipsos_mmnyt_processed_release.dta")) %>%
  mutate( year=2020,
          country="United States",
          state = as.character(haven::as_factor(State_Recoded)),
          solidarity = 10 - prior_self_over_soc,
          zsolidarity = weighted.scale(solidarity, Weightvar, na.rm=TRUE),
          znationalism = weighted.scale(prior_national_over_global, Weightvar, na.rm = TRUE),
          zluck_unfair = weighted.scale(luck_unfair_agree, Weightvar, na.rm = TRUE),
          zcompassion = weighted.scale(compassion_agree, Weightvar, na.rm = TRUE),
          znoborders = weighted.scale(noborders_agree, Weightvar, na.rm = TRUE),
          zluck_belief = weighted.scale(luck_determ_agree, Weightvar, na.rm = TRUE),
          redistribution = gov_reduce_inequality_agree,
          zredistribution = weighted.scale(redistribution, Weightvar, na.rm = TRUE),
          politics = as.character(haven::as_factor(GDW6)),
          republican = as.numeric(ifelse(politics!="Prefer not to answer", 
                                         politics=="Republican",
                                         NA)),
          female = as.numeric(resp_gender==2),
  ) %>% left_join(wavedate_df) %>%
  filter(!is.na(wavedt)) %>%
  filter(!is.na(corona_prime))
```

Merging in the confirmed cases by state.
```{r}
confirmed <- read.csv(here::here("data","corona_status_March-28.csv")) %>%
  mutate(confirmed_cases = confirmed/pop2019 * 100000000) %>%
  select(state, confirmed_cases)
ipsos <- ipsos %>% left_join(confirmed, by="state")
```

I create a new variable splitting the states by whether they have above or below 
(population-weighted) median exposure to the virus by the in-state number of
confirmed cases.
```{r}
ipsos <- ipsos %>% mutate( high_confirmed = 
                             as.numeric(confirmed_cases > wtd.quantile(confirmed_cases,
                                                                       0.5, 
                                                                       weight = Weightvar)))
wtd.quantile(ipsos$confirmed_cases, 0.5, weight=ipsos$Weightvar
)
```
# Romano-Wolf corrections, Luck Unfair

I have Wolf's original `p.val.adj` code for doing the corrections. What I need is a function
that I can supply to R's `boot` command to return the relevant t-statistics on bootstrapped
data.

```{r}
bs_luckunfair <- function(data, Rb=999, new_seed=431242412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  l1t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l2t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l3t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l4t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l5t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l6t <- hdata %>% lm(zluck_unfair ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(l1t)[['Xpolitical']], Xincome = coef(l2t)[['Xincome']], 
                    Xeducation = coef(l3t)[['Xeducation']], Xgender = coef(l4t)[['Xgender']], 
                    Xretirement = coef(l5t)[['Xretirement']], Xconfirmed = coef(l6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(zluck_unfair - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(zluck_unfair - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(zluck_unfair - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(zluck_unfair - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(zluck_unfair - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(zluck_unfair - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30,  theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}
```


Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw1 <- bs_luckunfair(ipsos, Rb = NBOOTSTRAPS)
rw1 %>% knitr::kable(digits=3)
```

# Romano Wolf adjustment, Solidarity
```{r}
bs_solidarity <- function(data, Rb=999, new_seed=32432412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  s1t <- hdata %>% lm(zsolidarity ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s2t <- hdata %>% lm(zsolidarity ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s3t <- hdata %>% lm(zsolidarity ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s4t <- hdata %>% lm(zsolidarity ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s5t <- hdata %>% lm(zsolidarity ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s6t <- hdata %>% lm(zsolidarity ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(s1t)[['Xpolitical']], Xincome = coef(s2t)[['Xincome']], 
                    Xeducation = coef(s3t)[['Xeducation']], Xgender = coef(s4t)[['Xgender']], 
                    Xretirement = coef(s5t)[['Xretirement']], Xconfirmed = coef(s6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(zsolidarity - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(zsolidarity - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(zsolidarity - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(zsolidarity - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(zsolidarity - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(zsolidarity - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30, theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}
```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw2 <- bs_solidarity(ipsos, Rb = NBOOTSTRAPS)
rw2 %>% knitr::kable(digits=3)
```

# Interaction effects on nationalism
```{r}
bs_nationalism <- function(data, Rb=999, new_seed=329172412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  s1t <- hdata %>% lm(znationalism ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s2t <- hdata %>% lm(znationalism ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s3t <- hdata %>% lm(znationalism ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s4t <- hdata %>% lm(znationalism ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s5t <- hdata %>% lm(znationalism ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s6t <- hdata %>% lm(znationalism ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(s1t)[['Xpolitical']], Xincome = coef(s2t)[['Xincome']], 
                    Xeducation = coef(s3t)[['Xeducation']], Xgender = coef(s4t)[['Xgender']], 
                    Xretirement = coef(s5t)[['Xretirement']], Xconfirmed = coef(s6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(znationalism - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(znationalism - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(znationalism - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(znationalism - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(znationalism - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(znationalism - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30, theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}
```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw3 <- bs_nationalism(ipsos, Rb = NBOOTSTRAPS)
rw3 %>% knitr::kable(digits=3)
```



# Interaction effects on Compassion

```{r}
bs_compassion <- function(data, Rb=999, new_seed=431242412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  l1t <- hdata %>% lm(zcompassion ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l2t <- hdata %>% lm(zcompassion ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l3t <- hdata %>% lm(zcompassion ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l4t <- hdata %>% lm(zcompassion ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l5t <- hdata %>% lm(zcompassion ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l6t <- hdata %>% lm(zcompassion ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(l1t)[['Xpolitical']], Xincome = coef(l2t)[['Xincome']], 
                    Xeducation = coef(l3t)[['Xeducation']], Xgender = coef(l4t)[['Xgender']], 
                    Xretirement = coef(l5t)[['Xretirement']], Xconfirmed = coef(l6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(zcompassion - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(zcompassion - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(zcompassion - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(zcompassion - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(zcompassion - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(zcompassion - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30,  theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}

```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw2v <- bs_compassion(ipsos, Rb = NBOOTSTRAPS)
rw2v %>% knitr::kable(digits=3)
```


# Interaction effects on "No borders"

```{r}
bs_noborders <- function(data, Rb=999, new_seed=431242412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  l1t <- hdata %>% lm(znoborders ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l2t <- hdata %>% lm(znoborders ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l3t <- hdata %>% lm(znoborders ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l4t <- hdata %>% lm(znoborders ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l5t <- hdata %>% lm(znoborders ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l6t <- hdata %>% lm(znoborders ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(l1t)[['Xpolitical']], Xincome = coef(l2t)[['Xincome']], 
                    Xeducation = coef(l3t)[['Xeducation']], Xgender = coef(l4t)[['Xgender']], 
                    Xretirement = coef(l5t)[['Xretirement']], Xconfirmed = coef(l6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(znoborders - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(znoborders - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(znoborders - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(znoborders - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(znoborders - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(znoborders - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30,  theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}

```


Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw3v <- bs_noborders(ipsos, Rb = NBOOTSTRAPS)
rw3v %>% knitr::kable(digits=3)
```


# Interaction effects on "Luck belief"

```{r}
bs_luckbelief <- function(data, Rb=999, new_seed=431242412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  l1t <- hdata %>% lm(zluck_belief ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l2t <- hdata %>% lm(zluck_belief ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l3t <- hdata %>% lm(zluck_belief ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l4t <- hdata %>% lm(zluck_belief ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l5t <- hdata %>% lm(zluck_belief ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  l6t <- hdata %>% lm(zluck_belief ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(l1t)[['Xpolitical']], Xincome = coef(l2t)[['Xincome']], 
                    Xeducation = coef(l3t)[['Xeducation']], Xgender = coef(l4t)[['Xgender']], 
                    Xretirement = coef(l5t)[['Xretirement']], Xconfirmed = coef(l6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(zluck_belief - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(zluck_belief - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(zluck_belief - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(zluck_belief - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(zluck_belief - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(zluck_belief - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30,  theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}

```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw1v <- bs_luckbelief(ipsos, Rb = NBOOTSTRAPS)
rw1v %>% knitr::kable(digits=3)
```

# Interaction effects on redistribution
```{r}
bs_redistribution_heterogeneity <- function(data, Rb=999, new_seed=32432412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  s1t <- hdata %>% lm(zredistribution ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s2t <- hdata %>% lm(zredistribution ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s3t <- hdata %>% lm(zredistribution ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s4t <- hdata %>% lm(zredistribution ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s5t <- hdata %>% lm(zredistribution ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s6t <- hdata %>% lm(zredistribution ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(s1t)[['Xpolitical']], Xincome = coef(s2t)[['Xincome']], 
                    Xeducation = coef(s3t)[['Xeducation']], Xgender = coef(s4t)[['Xgender']], 
                    Xretirement = coef(s5t)[['Xretirement']], Xconfirmed = coef(s6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(zredistribution - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(zredistribution - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(zredistribution - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(zredistribution - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(zredistribution - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(zredistribution - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30, theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}
```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw4 <- bs_redistribution_heterogeneity(ipsos, Rb = NBOOTSTRAPS)
rw4 %>% knitr::kable(digits=3)
```



# Interaction effects for health care

```{r}
bs_healthcare_heterogeneity <- function(data, Rb=999, new_seed=32432412) {
  set.seed(new_seed)
  hdata <- data %>% mutate(Xpolitical = republican * corona_prime,
                           Xincome = highinc * corona_prime,
                           Xeducation = higheduc * corona_prime,
                           Xgender = female * corona_prime,
                           Xretirement = retirement_age * corona_prime,
                           Xconfirmed = high_confirmed * corona_prime)
  s1t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xpolitical + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s2t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xincome + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s3t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xeducation + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s4t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xgender + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s5t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xretirement + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  s6t <- hdata %>% lm(fed_univ_healthcare ~ corona_prime + Xconfirmed + retirement_age + female + highinc + 
                        republican + higheduc +
                        child + alone + urban + high_confirmed +
                        northeast + midwest + south, data=., weights=Weightvar)
  actual_betas <- c(Xpolitical = coef(s1t)[['Xpolitical']], Xincome = coef(s2t)[['Xincome']], 
                    Xeducation = coef(s3t)[['Xeducation']], Xgender = coef(s4t)[['Xgender']], 
                    Xretirement = coef(s5t)[['Xretirement']], Xconfirmed = coef(s6t)[['Xconfirmed']])
  
  
  bsfn <- function(data, indices, theta, enforce) {
    datab <- data[indices,]
    l1 <- datab %>% lm(fed_univ_healthcare - enforce*Xpolitical*theta[['Xpolitical']] ~ 
                         corona_prime + Xpolitical + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l2 <- datab %>% lm(fed_univ_healthcare - enforce*Xincome*theta[['Xincome']] ~ 
                         corona_prime + Xincome + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l3 <- datab %>% lm(fed_univ_healthcare - enforce*Xeducation*theta[['Xeducation']] ~ 
                         corona_prime + Xeducation + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l4 <- datab %>% lm(fed_univ_healthcare - enforce*Xgender*theta[['Xgender']] ~ 
                         corona_prime + Xgender + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l5 <- datab %>% lm(fed_univ_healthcare - enforce*Xretirement*theta[['Xretirement']] ~ 
                         corona_prime + Xretirement + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    l6 <- datab %>% lm(fed_univ_healthcare - enforce*Xconfirmed*theta[['Xconfirmed']] ~ 
                         corona_prime + Xconfirmed + retirement_age + female + highinc + 
                         republican + higheduc +
                         child + alone + urban + high_confirmed +
                         northeast + midwest + south, data=., weights=Weightvar)
    ret <- c(
      Xpolitical = coef(l1)[['Xpolitical']] / sqrt(diag(vcovHC(l1, type = "HC1")))[['Xpolitical']],
      Xincome =  coef(l2)[['Xincome']] / sqrt(diag(vcovHC(l2, type = "HC1")))[['Xincome']],
      Xeducation =  coef(l3)[['Xeducation']] / sqrt(diag(vcovHC(l3, type = "HC1")))[['Xeducation']],
      Xgender =  coef(l4)[['Xgender']] / sqrt(diag(vcovHC(l4, type = "HC1")))[['Xgender']],
      Xretirement =  coef(l5)[['Xretirement']] / sqrt(diag(vcovHC(l5, type = "HC1")))[['Xretirement']],
      Xconfirmed =  coef(l6)[['Xconfirmed']] / sqrt(diag(vcovHC(l6, type = "HC1")))[['Xconfirmed']]
    )
    abs(ret)
  }
  t0 <- bsfn(hdata, 1:nrow(hdata), theta=actual_betas, enforce=0)
  b_obj <- boot(hdata, bsfn, R=Rb, parallel="multicore", ncpus=30, theta=actual_betas, enforce=1)
  p.val.adj(t0, b_obj$t)
}
```

Now, for calculating the bootstrapped p-values and with the Romano-Wolf adjustment.
```{r}
rw5 <- bs_healthcare_heterogeneity(ipsos, Rb = NBOOTSTRAPS)
rw5 %>% knitr::kable(digits=3)
```

# sessionInfo()

```{r}
sessionInfo()
```

